Summary of changes

### 2018-02-27 summary_of_changes.tex
summary

\sloppy

\vskip0.3cm
\hrule width11.5cm height1pt % black line
\vskip0.1cm
{\it Tammy Riklin Raviv}\\[0.05cm]
{\small The Department of Electrical and Computer Engineering} \\[0.07cm]
{\small Ben-Gurion University of the Negev} \\
{\small Beer-Shava 84105 {\hskip6pt} ISRAEL}\\[0.1cm]
{\scriptsize Tel: +972 8 642 8812}\hspace{8pt}
               {\scriptsize Fax: +972 8 647 2947}\\
{\scriptsize E-mail: \hspace{1pt} rrtammy@ee.bgu.ac.il}\\

\vspace{-0.7cm}
\hfill February 2018

IEEE Transactions on Pattern Analysis and Machine Intelligence
\vspace{0.2cm}

Dear Prof. Dickinson,

@@

It is our pleasure to submit a new manuscript entitled  ``{\it Accelerated Magnetic Resonance Imaging by Generative Adversarial Neural Networks}'' for
consideration by the IEEE Transactions on Pattern Analysis and Machine Intelligence journal. 
The manuscript is co-authored by Ohad Shitrit and Tammy Riklin Raviv.

@@

Thank you for the consideration of this manuscript.

We look forward to hearing from you.

\vspace{1cm}

Sincerely,

@@

Tammy Riklin-Raviv

>>>>

\title{Summary of changes}
\maketitle
Manuscript name: Accelerated Magnetic Resonance Imaging by Generative Adversarial Neural Networks
\vspace{0.2cm}

@@

@@

@@

Ohad Shitrit\\
Tammy Riklin Raviv
